Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-05 paper_jasa.tex
comments on turk workers' skill test

There are some noticeable exceptions to this rule. In experiment 1, when $\beta=5, n=300, \sigma=12, rep=3$, people tended to pick the plot with the second smallest $p$-value.  Same experiment, when $\beta=0, n=100, \sigma=5, rep=1$ people overwhelming chose a plot with much larger $p$-value. For several of these exceptions, along with several easy lineups, we followed up with a new experiment using an eye-tracker to examine what the observers were looking at in making their choices \citep{zhao2012}.
(Lineups chosen for the eye-tracker experiment were in experiment 1, (1) $n=100, \beta=3, \sigma=5, rep=1$ (2) $n=100, \beta=5, \sigma=5, rep=1$ (3) $n=100, \beta=10, \sigma=12, rep=1$ and (4) $n=300, \beta=5, \sigma=5, rep=1$, and in experiment 2, (5) $n=100, \beta=3.5, \sigma=12, rep=1$ (6) $n=100, \beta=4.5, \sigma=12, rep=2$ (7) $n=300, \beta=1, \sigma=5, rep=1$ and (8) $n=300, \beta=1, \sigma=5, rep=2$.)

@@

\green{Mention the possibility of a visual skills test, to select the workers that are better qualified, to implement the lineup protocol in practice. Along the lines of the Army tests that Susan brought to the working group.

>>>>

There are some noticeable exceptions to this rule. In experiment 1, when $\beta=5, n=300, \sigma=12, rep=3$, people tended to pick the plot with the second smallest $p$-value.  Same experiment, when $\beta=0, n=100, \sigma=5, rep=1$ people overwhelming chose a plot with much larger $p$-value. For several of these exceptions, along with several easy lineups, we followed up with a new experiment using an eye-tracker to examine what the observers were looking at in making their choices \citep{zhao:2012}.
(Lineups chosen for the eye-tracker experiment were in experiment 1, (1) $n=100, \beta=3, \sigma=5, rep=1$ (2) $n=100, \beta=5, \sigma=5, rep=1$ (3) $n=100, \beta=10, \sigma=12, rep=1$ and (4) $n=300, \beta=5, \sigma=5, rep=1$, and in experiment 2, (5) $n=100, \beta=3.5, \sigma=12, rep=1$ (6) $n=100, \beta=4.5, \sigma=12, rep=2$ (7) $n=300, \beta=1, \sigma=5, rep=1$ and (8) $n=300, \beta=1, \sigma=5, rep=2$.)

@@

\green{Mention the possibility of a visual skills test, to select the workers that are better qualified, to implement the lineup protocol in practice. Along the lines of the Army tests that Susan brought to the working group. \blue{While recruiting subjects from the Amazon Mechanical Turk web site we did not put any restriction on the skill levels of the subjects. Thus anyone from any background could participate the experiment. It would be interesting to see how well the trained subjects performs. Many pilot studies with advanced knowledge of statistical graphics as well as statistics indicates that the performance is very good for trained subjects. One of our future work would be to examine this in details. For this we are planning to trained Turk subjects with specific graphics and educate them what pattern a specific graphics may show. After being trained they may have to pass the qualification test before participating the experiment. Even though we did not do this, it is very common to Turk subjects to go through this process for various other tasks they do in the Turk web site.}.
